On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-11-17 paper/paper.tex
typos

\begin{itemize}
  \item A representation of pattern matching in a Haskell EDSL (Section~\ref{sec:PatRep})
  \item A representation of lambdas (Section~\ref{sec:LamRep}) in the EDSL, taking advantage of
  the fact that both pattern matching and tail recursion are already captured in
  the EDSL.
\item A GHC Core plugin which transforms a subset of standard Haskell code
  into this EDSL for pattern matching, extended with tail recursion,
  lambdas and primitive operations (Section~\ref{sec:CorePlugin})
\item An implementation of a interpreter for the "standard" semantics of the EDSL (Section~\ref{sec:StdSemantics}).
% \item An outline of a C backend for this EDSL (Section~\ref{sec:CBackend}).
\end{itemize}

@@

Briefly, a algebraic type \ttt{T} with an automatically generated \ttt{ERep}
instance is given a representation in terms of \ttt{Either}, \ttt{(,)}, \ttt{()}
and \ttt{Void}.  This "standardized" type representation is given by \ttt{ERepTy
T}. \ttt{ERepTy} is a type family associated to the type class \ttt{ERep}. This
type will be called the \textit{canonical type} of \ttt{T}.

>>>>

\begin{itemize}
  \item A representation of pattern matching in a Haskell EDSL (Section~\ref{sec:PatRep})
  \item A representation of lambdas (Section~\ref{sec:LamRep}) in the EDSL, taking advantage of
  the fact that both pattern matching and tail recursion are already captured in
  the EDSL.
  \item A GHC Core plugin which transforms a subset of standard Haskell code
  into this EDSL for pattern matching, extended with tail recursion,
  lambdas and primitive operations (Section~\ref{sec:CorePlugin})
  \item An implementation of an interpreter for the "standard" semantics of the EDSL (Section~\ref{sec:StdSemantics}).
% \item An outline of a C backend for this EDSL (Section~\ref{sec:CBackend}).
\end{itemize}

@@

Briefly, an algebraic type \ttt{T} with an automatically generated \ttt{ERep}
instance is given a representation in terms of \ttt{Either}, \ttt{(,)}, \ttt{()}
and \ttt{Void}.  This "standardized" type representation is given by \ttt{ERepTy
T}. \ttt{ERepTy} is a type family associated to the type class \ttt{ERep}. This
type will be called the \textit{canonical type} of \ttt{T}.
